---
title: "Final Project Divvy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Divvy Dataset

Historical trip data available to the public
Here you'll find Divvy's trip data for public use. So whether you're a policy maker, transportation professional, web developer, designer, or just plain curious, feel free to download it, map it, animate it, or bring it to life!
Note that we'll be releasing trip data twice a year: once following the end of calendar Q2 and once following the end of calendar Q4. This data is provided according to the Divvy Data License Agreement.

The Data
Each trip is anonymized and includes:
  *Trip start day and time
  * Trip end day and time
  *Trip start station
  *Trip end station
  *Rider type (Member or 24-Hour Pass User)
  *If a Member trip, it will also include Member's gender and year of birth
Click the buttons on the right side of the page to download the available data sets. The folders also include a shapefile of our stations (and you can get live station info on our station JSON feed).


##Read the Dataset
Change the file path when working with a different computer
```{r cars}
divvy_trips_2016_04 <- read.csv(file="C:/Users/dglownia/Documents/GitHub/CSC-465-Data-Visualization-Divvy-Final-Project/Dataset/Divvy_Trips_2016_Q1Q2/Divvy_Trips_2016_04.csv",head=TRUE,sep=",")
divvy_trips_2016_05 <- read.csv(file="C:/Users/dglownia/Documents/GitHub/CSC-465-Data-Visualization-Divvy-Final-Project/Dataset/Divvy_Trips_2016_Q1Q2/Divvy_Trips_2016_05.csv",head=TRUE,sep=",")
divvy_trips_2016_06 <- read.csv(file="C:/Users/dglownia/Documents/GitHub/CSC-465-Data-Visualization-Divvy-Final-Project/Dataset/Divvy_Trips_2016_Q1Q2/Divvy_Trips_2016_06.csv",head=TRUE,sep=",")
divvy_stations_2016_q1q2 <- read.csv(file="C:/Users/dglownia/Documents/GitHub/CSC-465-Data-Visualization-Divvy-Final-Project/Dataset/Divvy_Trips_2016_Q1Q2/Divvy_Stations_2016_Q1Q2.csv",head=TRUE,sep=",")


```
