---
title: "Homework 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Divvy Dataset

Historical trip data available to the public
Here you'll find Divvy's trip data for public use. So whether you're a policy maker, transportation professional, web developer, designer, or just plain curious, feel free to download it, map it, animate it, or bring it to life!
Note that we'll be releasing trip data twice a year: once following the end of calendar Q2 and once following the end of calendar Q4. This data is provided according to the Divvy Data License Agreement.

The Data
Each trip is anonymized and includes:
  *Trip start day and time
  *Trip end day and time
  *Trip start station
  *Trip end station
  *Rider type (Member or 24-Hour Pass User)
  *If a Member trip, it will also include Member's gender and year of birth
Click the buttons on the right side of the page to download the available data sets. The folders also include a shapefile of our stations (and you can get live station info on our station JSON feed).


##Read the Dataset
Change the file path when working with a different computer
```{r cars}

April = read.table("C:/Users/dglownia/Desktop/divvy_merge.txt",  header = TRUE)

#April <- read.csv(file="C:/Users/dglownia/Documents/GitHub/CSC-465-Data-Visualization-Divvy-Final-Project/Dataset/Divvy_Trips_2016_Q1Q2/Divvy_Trips_2016_04.csv",head=TR#UE,sep=",")

```




```{r}

April$age <- (2016 - April$birthyear)

April$TripDurationHours <- floor(April$tripduration/60)

April$gender <- ifelse(April$usertype != "Customer", April$gender, 1 )

April <- April[!(April$gender == 1),]

April$gender <- ifelse(April$gender==2, "Female", "Male" )

```


```{r}

April$TripDurationHours <- paste(floor(April$tripduration/60),"hr")

April$ageCatagorical <- paste("Age: ", (floor(April$age/10) *10))

```

##Male vs Female ride habits

```{r}

library(xtable)
library(dplyr)

#Create new data frame for positive (spending) values
gender <- April %>% select(gender, ageCatagorical, TripDurationHours, tripduration) %>%
  group_by(gender, ageCatagorical, TripDurationHours) %>%
  summarize(tripduration = sum(tripduration, na.rm=FALSE))

age <- April %>% select(gender, TripDurationHours, tripduration) %>%
  group_by(gender, TripDurationHours) %>%
  summarize(tripduration = sum(tripduration, na.rm=FALSE))

```



```{r}

library(treemap)
treemap(gender, #Your data frame object
        index=c("gender","ageCatagorical", "TripDurationHours"),  #A list of your categorical variables
        vSize = "tripduration",  #This is your quantitative variable
        type="index", #Type sets the organization and color scheme of your treemap
        palette = "Pastel1",  #Select your color palette from the RColorBrewer presets or make your own.
        title="Male and Female Ride Habits", #Customize your title
        fontsize.title = 14 #Change the font size of the title
        )



```

##Food Services

```{r}

food = read.csv(file="C:/Users/dglownia/Desktop/food.csv",head=TRUE,sep=",")
states = read.csv(file="C:/Users/dglownia/Desktop/states.csv",head=TRUE,sep=",")

region = tolower(states$ALASKA)
value97 = states$X1763
value00 = states$X1849
value07 = states$X1996

foodservices97 = data.frame(region, value97 )
foodservices97 <- unique(foodservices)

foodservices00 = data.frame(region, value00 )
foodservices00 <- unique(foodservices)

foodservices07 = data.frame(region, value07 )
foodservices07 <- unique(foodservices)
```


```{r}

library(choroplethr)

?df_pop_state
data(df_pop_state)

?state_choropleth
state_choropleth(df_pop_state)


```

```{r}

data(df_pop_state)
state_choropleth(foodservices97, 
                 title  = "US Food Services 1997", 
                 legend = "Food Services by number")

```

```{r}

data(df_pop_state)
state_choropleth(foodservices00, 
                 title  = "US Food Services 2000", 
                 legend = "Food Services by number")

```

```{r}

data(df_pop_state)
state_choropleth(foodservices07, 
                 title  = "US Food Services 1997", 
                 legend = "Food Services by number")

```

